Giant Low Surface Brightness Galaxies As Merger Remnants

### 2017-01-26 final/ms.tex
minor tweaks

\begin{figure*}
\epsscale{.4}
\plotone{Color_Magnitu_Diagram.eps}\plotone{Faber_Jackson_Relation.eps}\\
\plotone{Fundamental_Plane.eps}\plotone{mg_sigma.eps}
\epsscale{1}
\caption{
Top Left:  The color-magnitude diagram for 141,000 galaxies of similar redshift and magnitude as Malin~2 and UGC~6614.
Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.
Left:  The $r$-band fundamental plane from SDSS along with our GLSB galaxies and best-fit line.
Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.
Contours are drawn which enclose 5\% to 85\% of the data with 20\% steps.
 From the point of view of the SDSS data reduction pipeline, GLSB galaxies appear as relatively red elliptical galaxies on the red-sequence.
\label{elliptical_relations}}
\end{figure*}

>>>>

\begin{figure*}
\epsscale{.4}
\plotone{Color_Magnitu_Diagram.eps}\plotone{Faber_Jackson_Relation.eps}\\
\plotone{Fundamental_Plane.eps}\plotone{mg_sigma.eps}
\epsscale{1}
\caption{
Top Left:  The color-magnitude diagram for 141,000 galaxies of similar redshift and magnitude as Malin~2 and UGC~6614.
Top Right:  The Faber-Jackson relation for 45,700 SDSS galaxies, along with a best-fit line.
Bottom Left:  The $r$-band fundamental plane from SDSS along with our GLSB galaxies and best-fit line. 
UGC~6614 is a slight outlier, but still within the 85\% contour.
Bottom Right:  The relation between central velocity dispersion and the Mg2 absorption feature.
Malin~1 is appears to be a metal-rich outlier. 
Contours are drawn which enclose 5\% to 85\% of the data with 20\% steps.
 From the point of view of the SDSS data reduction pipeline, GLSB galaxies appear as relatively red elliptical galaxies on the red-sequence.
\label{elliptical_relations}}
\end{figure*}
